---
title: 'Section 3: Data Explanatory Analysis'
author: "Lan Nguyen (6687547) | Lisa Verlare (6929699) | Nguyen Thuy Duong (6827209)"
output: 
  html_document:
    toc: true
    toc_depth: 3
    toc_float: true
    number_sections: true
editor_options: 
  chunk_output_type: console
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = F)
```

```{r packages, include=FALSE}
library(haven)
library(tidyverse)
library(dplyr)
library(clubSandwich)
library(kableExtra)
library(vtable)
library(ggpubr)
library(gridExtra)
library(ggplot2)
library(Hmisc) # statistic table format 
library(strucchange)  #Chow test
library(margins) # logit marginal effect
library(sandwich) # correct downward-biased standard errors
library(corrplot)
library(RColorBrewer)
library(webshot)
webshot::install_phantomjs()
library(magick)
library(psych)
library(ggpubr)
```


# Data Preparation (Lisa)

The first part of this data preparation section consists of preparations to join the data sets together for more efficient coding and several functions are used to clean up the data.

The second part of this section consists of a small amount of variable descriptions and will produce a table with all variables.

The third part of this section shows a small sample description and the fourth saves the separate data sets again, in order to easily find each year.

```{r data}
# import the data sets from the data folder
year1999 <- read_dta("data/base99.dta")
year2000 <- read_dta("data/base00.dta")
year2001 <- read_dta("data/base01.dta")
year2002 <- read_dta("data/base02.dta")
```

```{r tidy}
# Look at the data to see whether the data sets are tidy (i.e., one value in a 
# cell) and does not need any adjustment in terms of needing to separate cells 
# or columns
head(year1999)
head(year2000)
head(year2001)
head(year2002)
```

```{r missing}
# Checking for missing values
sum(is.na(year1999))
sum(is.na(year2000))
sum(is.na(year2001))
sum(is.na(year2002))
```

**Conclusion: **

    * Each dataset has 25 columns
  
    * Each dataset has one entry per column and rows are clearly observations for separate students
  
    * Each dataset has 0 missing values. 

Next, we merge the data sets in order to make some changes that are not specific to a year.
```{r columns}
# Check whether the columns are the same, otherwise adjustments will have to be 
# made before they can be joined together
identical(colnames(year1999), colnames(year2000))
identical(colnames(year1999), colnames(year2001))
identical(colnames(year1999), colnames(year2002))
```

Each data set has identical column names, which means that each data set has the same sort of observations. Hence, we can merge the data sets together.

```{r merge}
# Merging / Joining all data sets into one data set to make the 
# cleaning up process easier
data <- full_join(year1999, year2000)
data <- full_join(data, year2001)
data <- full_join(data, year2002)
```


Now that the data sets are merged together, we can efficiently clean up the data set.

```{r rename}
# Renaming variables to make them more understandable
data <- data %>%
  rename(
    siblings = m_ahim,
    immigrant = ole5, 
    father_educ = educav,
    mother_educ = educem,
    bagrut_status = zakaibag,
    school_religious = semrel,
    school_arab = semarab
  )
```

The `year` variable now indicates a date with '00' instead of 2000. Otherwise, it could be confusing when filtering. 
```{r years}
# Naming year entries according to their full year, which will make it easier 
# to filter out years and make them more understandable
data <- data %>%
  mutate(
    year = replace(year, year == 99, 1999),
    year = replace(year, year == 0, 2000),
    year = replace(year, year == 1, 2001),
    year = replace(year, year == 2, 2002)
    )
```

The authors have also coded additional variables.
```{r variables}
# Adding and removing variables for the replication process

data <- data %>% 
   mutate(
      # at least 4 siblings dummy
      siblings_4 = as.numeric(siblings >= 4),
      
      # Categorizing pair and school_id as a factor
      pair = as.factor(pair),
      school_id = as.factor(school_id)
      ) %>%
  
  # removing variables we will not be using in our research
  select(
    -student_id, -att18, -att20, -att22, -att24, -awr18, -awr20, -awr22, -awr24,
    -achv_math, -achv_eng, -achv_hib
    )
```

This variable is for our own analysis.
```{r siblings}
# Creating a siblings variable into a categorical variable
data$sib_category <- as.factor(
  ifelse(data$siblings == 1, "1",
         ifelse(data$siblings == 2, "2",
                ifelse(data$siblings == 3, "3",
                       ifelse(data$siblings == 4, "4", "4+"
                              )
                       )
                )
         )
  )

```

We now separate the data sets again, to make individual variables per year.

```{r save}
# Saving the final data, in case we will use another Rmd file or for any other
# purpose
saveRDS(data, file = "data/full_data.Rdata")

# splitting up the datasets again per year and saving them to  use in other Rmd
# files
data_1999 <- data %>%
  filter(year == 1999)

data_2000 <- data %>%
  filter(year == 2000)

data_2001 <- data %>%
  filter(year == 2001)

data_2002 <- data %>%
  filter(year == 2002)
```


```{r quartiles}
# create quantile dummies for 1999
data_1999 <- data_1999 %>% 
  mutate(
    
    # quartiles
    ls_100 = as.numeric(lagscore >= quantile(lagscore, 0.75)),
    ls_75 = as.numeric(
      lagscore >= quantile(lagscore, 0.50) &
        lagscore < quantile(lagscore, 0.75)
      ),
    ls_50 = as.numeric(
      lagscore >= quantile(lagscore, 0.25) & 
        lagscore < quantile(lagscore, 0.50)
      ),
    ls_25 =  as.numeric(lagscore < quantile(lagscore, 0.25)),
    
    # top and bottom marginal groups
    top_ls = ifelse(ls_75 == 1 | ls_100 == 1, 1, 0),
    bot_ls = ifelse(ls_25 == 1 | ls_50 == 1, 1, 0),
    
    # lagged score
    ls = lagscore
    )

# create quantile dummies for 2000
data_2000 <- data_2000 %>% 
  mutate(
    
    # quartiles
    ls_100 = as.numeric(lagscore >= quantile(lagscore, 0.75)),
    ls_75 = as.numeric(
      lagscore >= quantile(lagscore, 0.50) &
        lagscore < quantile(lagscore, 0.75)
      ),
    ls_50 = as.numeric(
      lagscore >= quantile(lagscore, 0.25) & 
        lagscore < quantile(lagscore, 0.50)
      ),
    ls_25 =  as.numeric(lagscore < quantile(lagscore, 0.25)),
    
    # top and bottom marginal groups
    top_ls = ifelse(ls_75 == 1 | ls_100 == 1, 1, 0),
    bot_ls = ifelse(ls_25 == 1 | ls_50 == 1, 1, 0),
    
    # lagged score
    ls = lagscore
    )

# create quantile, marginal top and bottom dummies for 2001
data_2001 <- data_2001 %>% 
  mutate(
    
    # quartiles
    ls_100 = as.numeric(lagscore >= quantile(lagscore, 0.75)),
    ls_75 = as.numeric(
      lagscore >= quantile(lagscore, 0.50) &
        lagscore < quantile(lagscore, 0.75)
      ),
    ls_50 = as.numeric(
      lagscore >= quantile(lagscore, 0.25) & 
        lagscore < quantile(lagscore, 0.50)
      ),
    ls_25 =  as.numeric(lagscore < quantile(lagscore, 0.25)),
    
    # top and bottom marginal groups
    top_ls = ifelse(ls_75 == 1 | ls_100 == 1, 1, 0),
    bot_ls = ifelse(ls_25 == 1 | ls_50 == 1, 1, 0),
    
    # lagged score
    ls = lagscore
         )

# create quantile, marginal top and bottom dummies for 2002
data_2002 <- data_2002 %>% 
  mutate(
    
    # quartiles
    ls_100 = as.numeric(lagscore >= quantile(lagscore, 0.75)),
    ls_75 = as.numeric(
      lagscore >= quantile(lagscore, 0.50) &
        lagscore < quantile(lagscore, 0.75)
      ),
    ls_50 = as.numeric(
      lagscore >= quantile(lagscore, 0.25) & 
        lagscore < quantile(lagscore, 0.50)
      ),
    ls_25 =  as.numeric(lagscore < quantile(lagscore, 0.25)),
    
    # top and bottom marginal groups
    top_ls = ifelse(ls_75 == 1 | ls_100 == 1, 1, 0),
    bot_ls = ifelse(ls_25 == 1 | ls_50 == 1, 1, 0),
    
    # lagged score
    ls = lagscore
         )
```

We will save the data sets in the folder *data*, because we have separated our code into multiple Rmd files. This will make it easy to access.

```{r}
# saving the data sets
saveRDS(data_1999, file = "data/data_1999.Rda")
saveRDS(data_2000, file = "data/data_2000.Rda")
saveRDS(data_2001, file = "data/data_2001.Rda")
saveRDS(data_2002, file = "data/data_2002.Rda")

```

## Variable Description (Lisa)
In this part we show a small variable description and generate a *Variable Description Table* that will be included in the paper. We look at the data in general, as this is in regards to variables, not years.

```{r class}
# Check what the class of each variable is
lapply(data, class)
```

```{r dummies}
# Check whether those we suspect to be dummies are actually dummies
summary(data)
```
**Conclusion: **

    * There are 12 variables that are numeric, of which 7 are binary dummies.
    * There are 3 variables that are factors

**Disclaimer:** The following table describes the data in general, not per year.

```{r Variable Description Table}
# input for the variable description table
text_tbl <- data.frame(
  Variables = c(
    "treated", "pair", "siblings", "boy", "immigrant", "father_educ", 
    "mother_educ", "bagrut_status", "lagscore", "school_religious", 
    "school_arab", "year", "ls_#", "siblings_4", "sib_group"
    ),

  Description = c(
    "Treatment indicator, i.e., treated (1) and treatment (0)",
    "Treatment pair. Each treated school is paired to an untreated school that 
    are most similar in characteristics.",
    "Number of siblings", 
    "Gender indicator, i.e., boy (1) and girl (0)", 
    "Immigrant indicator, i.e., immigrant (1) and non-immigrant (0)",
    "Father’s years of schooling", 
    "Mother’s years of schooling", 
    "Bagrut status, i.e., Bagrut (1) and no Bagrut (0)", 
    "Lagged Bagrut score, based on Bagrut rates from 1999", 
    "Indicator of Jewish religious school, i.e., Jewish religious (1) and 
    non-Jewish religious (0)", 
    "Indicator of Arab school, i.e., Arab (1) and non-Arab (0)",
    "Year indicator", 
    "Indicators of quantiles (25, 50, 75, 100), i.e., quantile (1) and not in 
    the quantile (0)",
    "Indicator whether the individual has 4 or more siblings, i.e. 4(+) siblings 
    (1) and less than 4 siblings (0)",
    "Categorical variable for the amount of siblings, ranging from 1-4+"
    )
)

# Creating the table
kbl(text_tbl, caption = "<b>Table 1: Variable Descripton</b>") %>%
  kable_classic(full_width = FALSE, html_font = "Times New Roman") %>%
  kable_styling(bootstrap_options = c("bordered", "basic")) %>%
  row_spec(0, bold = TRUE) %>%
  column_spec(1, bold = FALSE, border_right = TRUE, background = "lightgrey") %>%
  column_spec(2, width = "16cm") %>%
  footnote(
    general = c(
      "The table describes the variables in general, they are not year specific"
      ),
    footnote_as_chunk = T
  )
```

--------------------------------------------------------------------------------------------------------------------------------------

# Data Descriptives (Duong)

This section encompasses two parts, with the first one providing a replicated statistical description of the administrative dataset for the Panel A.2001 and Panel B.2002 of the Table 1. Sizes of different treatment groups are also compared. The second part statistically describes the relationship between variable of interests (siblings_4) and other variables in the sample data_2001.

## Replication Table 1

### Administrative Dataset 

```{r}
# All variables in the Experimental sample
summary(data)
```

---

### Panel A.2001

```{r}
# All variables in the treated year 2001 sample
summary(data_2001)

# Subset samples
  # Subset for boys
summary(subset(data_2001, boy == 1))
  # Subset for girls 
summary(subset(data_2001, boy == 0))
```

```{r}
# Comparing statistics of key variables in full sample and 2001 sample 

list("siblings" = summary(data$siblings),
     "siblings_2001" = summary(data_2001$siblings),
     "father_educ" = summary(data$father_educ),
     "father_educ_2001" = summary(data_2001$father_educ),
     "mother_educ_2001" = summary(data_2001$mother_educ),
     "mother_educ" = summary(data$mother_educ))
```

---

### Panel B.2000

```{r}
# All variables in the control year 2000 sample
summary(data_2000)

# Subset samples
  # Subset for boys
summary(subset(data_2000, boy == 1))
  # Subset for girls 
summary(subset(data_2000, boy == 0))
```

```{r}
# Comparing statistics of key variables in full sample and 2000 sample 

list("siblings" = summary(data$siblings),
     "siblings_2000" = summary(data_2000$siblings),
     "father_educ" = summary(data$father_educ),
     "father_educ_2000" = summary(data_2000$father_educ),
     "mother_educ_2000" = summary(data_2000$mother_educ),
     "mother_educ" = summary(data$mother_educ))
```

We compare the sizes of different treatment groups between samples and see that treatment groups are relatively equal in size.

```{r}
# Sample sizes
# Sizes of Treated vs Control groups in 
  #Full data set
data %>% group_by(treated) %>% count()

  # 2001 sample
  # Relatively equally distributed: control = 1876, treated = 1945
data_2001 %>% group_by(treated) %>% count()

  # 2000 sample
data_2000 %>% group_by(treated) %>% count()
```

```{r}
# Visualization
ggdensity(data, 
          x = "year", 
          fill = "treated",  
          palette = "jco")

p <- ggplot(data, aes(x = year,
                 y = ..count.., 
                 fill = as.factor(treated))) +
  geom_bar() +
  labs(y = "") +
  guides(fill=guide_legend(title="")) + 
  scale_fill_discrete(labels = c("Control","Treatment")) +
  theme_classic()


annotate_figure(p, 
                top = text_grob("Sizes of treated vs control groups across years ",
                color = "red", face = "bold", size = 12))
```

We want to see if students dropped out of the research. 
```{r}
# Gender distribution over year
data %>% group_by(boy) %>% count()
data_2001 %>% group_by(boy) %>% count()
data_2000 %>% group_by(boy) %>% count()
```

```{r}
# Visualization
ggdensity(data, 
          x = "year", 
          fill = "boy",  
          palette = "jco")

p <- ggplot(data, aes(x = year,
                 y = ..count.., 
                 fill = as.factor(boy))) +
  geom_bar() +
  labs(y = "") +
  guides(fill=guide_legend(title="")) + 
  scale_fill_discrete(labels = c("Girls","Boys")) +
  theme_classic()


annotate_figure(p, 
                top = text_grob("Number of boys and girls over year",
                color = "red", face = "bold", size = 12))
```

---

### Descriptive Statistics Table

This includes the code for creating a table illustrating the means and standard errors of individual variables in the whole sample and subset samples for the year 2001 and 2000. This is a partial replication of the Table 1. 

**Table 1: Panel A.2001**

```{r}
# dataframe to contain the means and standard errors
desc_table_01 <- data.frame(NULL)
desc_var <- c("bagrut_status", "school_arab", "school_religious",
               "father_educ", "mother_educ", "siblings", "immigrant",
               "lagscore", "siblings_4", "")

# for-loop to assign values into dataframe

  ## All observations
for(i in 1:10){
  
  # means of individual covariates
  mean <- mean(data_2001[[desc_var[i]]])
  
  # standard errors of individual covariates
  sd <- sd(data_2001[[desc_var[i]]])
  
  # number of observations
  obs <- nrow(data_2001)
  
  # assigning values to the table
  desc_table_01[i, 1] <- mean
  desc_table_01[i, 2] <- sd
  desc_table_01[10, 1] <- obs
  }

  ## Sample for boys
for (i in 1:10){
  
  # mean of the column 
  mean <- mean(subset(data_2001, boy == 1)[[desc_var[i]]])
    
  # standard errors of individual covariates
  sd <- sd(subset(data_2001, boy == 1)[[desc_var[i]]])
  
  # number of observations
  obs <- nrow(subset(data_2001, boy == 1))
    
  # assigning values to the table
  desc_table_01[i, 3] <- mean
  desc_table_01[i, 4] <- sd
  desc_table_01[10, 2] <- obs
  }

  ## Sample for girls
for (i in 1:10){
    
    # mean of the column 
  mean <- mean(subset(data_2001, boy == 1)[[desc_var[i]]])
    
  # standard errors of individual covariates
  sd <- sd(subset(data_2001, boy == 1)[[desc_var[i]]])
  
  # number of observations
  obs <- nrow(subset(data_2001, boy == 0))
    
  # assigning values to the table
  desc_table_01[i, 5] <- mean 
  desc_table_01[i, 6] <- sd
  desc_table_01[10, 3] <- obs
  }

# Formatting

  ## Renaming columns
colnames(desc_table_01) <- c(
  "All", "Boy sample", "Girl sample")
  
  ## Renaming rows
rownames(desc_table_01) <- c("Bagrut rate", "Arab school", "Religious school",  "Father's education", "Mother's_education", "Number of siblings", "Immigrant",  "Lagged score", "Siblings category", "Number of observations")

  ## Round values
desc_table_01 <- round(desc_table_01, 3)

# Print the results
desc_table_01
```


**Table 1: Panel B.2000**

```{r}
# dataframe to contain the means and standard errors
desc_table_00 <- data.frame(NULL)
desc_var <- c("bagrut_status", "school_arab", "school_religious",
               "father_educ", "mother_educ", "siblings", "immigrant",
               "lagscore", "siblings_4", "")

# for-loop to assign values into dataframe

  ## All observations
for(i in 1:10){
  
  # means of individual covariates
  mean <- mean(data_2000[[desc_var[i]]])
  
  # standard errors of individual covariates
  sd <- sd(data_2000[[desc_var[i]]])
  
  # number of observations
  obs <- nrow(data_2000)
  
  # assigning values to the table
  desc_table_00[i, 1] <- mean
  desc_table_00[i, 2] <- sd
  desc_table_00[10, 1] <- obs
  }

  ## Sample boys
for (i in 1:10){
  
  # mean of the column 
  mean <- mean(subset(data_2000, boy == 1)[[desc_var[i]]])
    
  # standard errors of individual covariates
  sd <- sd(subset(data_2000, boy == 1)[[desc_var[i]]])
  
  # number of observations
  obs <- nrow(subset(data_2000, boy == 1))
    
  # assigning values to the table
  desc_table_00[i, 3] <- mean
  desc_table_00[i, 4] <- sd
  desc_table_00[10, 2] <- obs
  }

  ## Sample for girls
for (i in 1:10){
    
  # mean of the column 
  mean <- mean(subset(data_2000, boy == 1)[[desc_var[i]]])
    
  # standard errors of individual covariates
  sd <- sd(subset(data_2000, boy == 1)[[desc_var[i]]])
  
  # number of observations
  obs <- nrow(subset(data_2000, boy == 0))
    
  # assigning values to the table
  desc_table_00[i, 5] <- mean 
  desc_table_00[i, 6] <- sd
  desc_table_00[10, 3] <- obs
  }

# Formatting

  ## Rename columns
colnames(desc_table_00) <- c(
  "All", "Boy sample", "Girl sample")

  ## Rename rows
rownames(desc_table_00) <- c(
  "Bagrut rate", "Arab school", "Religious school",  "Father's education", 
  "Mother's_education", "Number of siblings", "Immigrant",  "Lagged score", 
  "Siblings category", "Number of observations"
  )

  ## Round values
desc_table_00 <- round(desc_table_00, 3)

# Print results
desc_table_00
```

**Combined Descriptives Statistics Table**

```{r}
# Panel A. 2001
  ## print standard errors beside means
for (i in 1:9){
  desc_table_01[i, 1] <- paste(
    desc_table_01[i, 1], "<br>(", desc_table_01[i, 4], ")", sep = ""
    )
  desc_table_01[i, 2] <- paste(
    desc_table_01[i, 2], "<br>(", desc_table_01[i, 5], ")", sep = ""
    )
  desc_table_01[i, 3] <- paste(
    desc_table_01[i, 3], "<br>(", desc_table_01[i, 6], ")", sep = ""
    )
}
desc_table_01[, 1] <- linebreak(desc_table_01[, 1])
desc_table_01[, 2] <- linebreak(desc_table_01[, 2])
desc_table_01[, 3] <- linebreak(desc_table_01[, 3])

  ## remove columns of the standard errors 
desc_table_01 <- desc_table_01[-c(4,5,6)]
desc_table_01 


# Panel B.2000
  ## print standard errors beside means
for (i in 1:9){
  desc_table_00[i, 1] <- paste(
    desc_table_00[i, 1], "<br>(", desc_table_00[i, 4], ")", sep = ""
    )
  desc_table_00[i, 2] <- paste(
    desc_table_00[i, 2], "<br>(", desc_table_00[i, 5], ")", sep = ""
    )
  desc_table_00[i, 3] <- paste(
    desc_table_00[i, 3], "<br>(", desc_table_00[i, 6], ")", sep = ""
    )
}
desc_table_00[, 1] <- linebreak(desc_table_00[, 1])
desc_table_00[, 2] <- linebreak(desc_table_00[, 2])
desc_table_00[, 3] <- linebreak(desc_table_00[, 3])

  ## remove columns of the standard errors 
desc_table_00 <- desc_table_00[-c(4,5,6)]
desc_table_00 


# Merging Panel A + Panel B
desc_table <- rbind(desc_table_01, desc_table_00)


# Formating & Saving

  ## Renaming rows
rownames(desc_table) <- c("Bagrut rate", "Arab school", "Religious school",  
                          "Father's education", "Mother's education", 
                          "Number of siblings", "Immigrant",  "Lagged score", 
                          "Siblings category", "Number of observations", 
                          "Bagrut rate ", "Arab school ", "Religious school ",  
                          "Father's education ", "Mother's education ", 
                          "Number of siblings ", "Immigrant ",  
                          "Lagged score ", "Siblings category ", 
                          "Number of observations ")

  ## Adding headlines
desc_table %>%
    kable(
      format = "html",
      size = 14,
      escape = FALSE,
      caption = "<b>Table 2: Descriptive Statistics</b>",
      align = "c") %>%
    kable_classic(
      full_width = F, 
      html_font = "Times New Roman", 
      position = "left"
      ) %>%
    
   # For Panel A
    pack_rows(
      "Panel A. 2001", 1, 2, italic = TRUE, bold = FALSE, underline = TRUE
      ) %>%
    pack_rows("School covariates", 2, 3, bold = TRUE) %>%
    pack_rows("Micro covariates", 4, 10, bold = TRUE) %>%
 
   # For Panel B
    pack_rows(
      "Panel B. 2000", 11, 12, italic = TRUE, bold = FALSE, underline = TRUE, 
      hline_before = TRUE, hline_after = TRUE
      ) %>%
    pack_rows("School covariates", 12, 13, bold = TRUE) %>%
    pack_rows("Micro covariates", 14, 19, bold = TRUE) %>%
  
   # Adding footnotes for table 
  footnote(general = c(
    "Table columns report sample means and standard deviations (shown in parentheses).",
    "This is a replication of Table B1 (Angrist & Lavy, 2009, p. 1391)"
    ),
    footnote_as_chunk = T
    ) 
```

**Conclusion:**

    * Fewer observations are recorded in the year 2001 compared to 2000, which is due to the drop out of the 39th school. However, the difference is not significant and the size of the sample remains efficiently large. 
  
    * Number of boys and number of girls in the treatment group and control group are relatively similar and constant over year. There are no significant drop-outs.

---

## Univariate descriptives

Data descriptive and visualization of the descriptive for each variable for all samples.

```{r}
# Immigration status 
  # Most students are natives: 3578 compared to 243
data_2001 %>% group_by(immigrant) %>% count()
```


```{r Full data}
# Visualization
p <- ggplot(data = data) + labs(x = "", y = "") +
    theme_classic()

# School covariates 
grid.arrange(
  
  p + 
    geom_bar(mapping = aes(factor(school_arab)), 
             color="black", fill="white") +
    labs(title = "School covariates distribution (All)", 
         subtitle = "Arab school"),
  
  p + 
    geom_bar(aes(factor(school_religious)), 
             color="black", fill="white") +
    labs(subtitle = "Religious school")
)


# Micro-covariates
p1 <-  p + 
    geom_histogram(mapping = aes(siblings), 
                   color="black", fill="white") +
    labs(subtitle = "Number of siblings") 
  
p2 <- p + 
   geom_histogram(mapping = aes(father_educ),
                   color="black", fill="white") +
    labs(subtitle = "Father education (years)")
     
p3 <-  p + 
    geom_histogram(mapping = aes(mother_educ),
                   color="black", fill="white") +
    labs(subtitle = "Mother education (years)")

p4 <- p + 
    geom_bar(mapping = aes(factor(immigrant)), 
             color="black", fill="white") +
    labs(subtitle = "Immigration status")
  
p5 <- p + 
    geom_bar(mapping = aes(factor(siblings_4)), 
             color="black", fill="white") +
    labs(subtitle = "Sibling groups")

p6 <- p + geom_bar(mapping = aes(factor(boy)), 
                   color="black", fill="white") +
                  labs(subtitle = "Gender")
p7 <-  p + 
    geom_histogram(mapping = aes(lagscore), 
                   color="black", fill="white") +
    labs(subtitle = "Lagscore")

p <- ggarrange(p1, p2, p3, p4, p5, p6, p7)
annotate_figure(p,  
                top = text_grob("Microcovariates (Full data)",
                color = "red", face = "bold", size = 12))
```

```{r 2001}
# Visualization
p <- ggplot(data = data_2001) + labs(x = "", y = "") +
    theme_classic()

# School covariates 
grid.arrange(
  
  p + 
    geom_bar(mapping = aes(factor(school_arab)), 
             color="black", fill="white") +
    labs(title = "School covariates distribution (2001)", 
         subtitle = "Arab school"),
  
  p + 
    geom_bar(aes(factor(school_religious)), 
             color="black", fill="white") +
    labs(subtitle = "Religious school")
)


# Micro-covariates
p1 <-  p + 
    geom_histogram(mapping = aes(siblings), 
                   color="black", fill="white") +
    labs(subtitle = "Number of siblings") 
  
p2 <- p + 
   geom_histogram(mapping = aes(father_educ),
                   color="black", fill="white") +
    labs(subtitle = "Father education (years)")
     
p3 <-  p + 
    geom_histogram(mapping = aes(mother_educ),
                   color="black", fill="white") +
    labs(subtitle = "Mother education (years)")

p4 <- p + 
    geom_bar(mapping = aes(factor(immigrant)), 
             color="black", fill="white") +
    labs(subtitle = "Immigration status")
  
p5 <- p + 
    geom_bar(mapping = aes(factor(siblings_4)), 
             color="black", fill="white") +
    labs(subtitle = "Sibling groups")

p6 <- p + geom_bar(mapping = aes(factor(boy)), 
                   color="black", fill="white") +
                  labs(subtitle = "Gender")
p7 <-  p + 
    geom_histogram(mapping = aes(lagscore), 
                   color="black", fill="white") +
    labs(subtitle = "Lagscore")

p <- ggarrange(p1, p2, p3, p4, p5, p6, p7)
annotate_figure(p,  
                top = text_grob("Microcovariates (2001)",
                color = "red", face = "bold", size = 12))

```


```{r 2000}
# Visualization

# School covariates
p <- ggplot(data = data_2000) + labs(x = "", y = "") +
    theme(title = element_text(size=8, face="bold")) +
    theme_classic()

# School covariates 
grid.arrange(
  p + 
    geom_bar(mapping = aes(factor(school_arab)), 
             color="black", fill="white") +
    labs(title = "School covariates distribution (2000)", 
         subtitle = "Arab school"),
  
 p + 
    geom_bar(aes(factor(school_religious)), 
             color="black", fill="white") +
    labs(subtitle = "Religious school")
)


# Micro-covariates
p1 <- p + geom_histogram(mapping = aes(siblings), 
                         color="black", fill="white") + 
                        labs(subtitle = "Number of siblings")
  
 
p2 <- p + geom_histogram(mapping = aes(father_educ),
                         color="black", fill="white") +
                        labs(subtitle = "Father education (years)")

p3 <- p + geom_histogram(mapping = aes(mother_educ),
                         color="black", fill="white") +
                        labs(subtitle = "Mother education (years)")
  
p4 <- p + geom_bar(mapping = aes(factor(immigrant)),
                   color="black", fill="white") +
                  labs(subtitle = "Immigration status")

p5 <- p + geom_bar(mapping = aes(factor(siblings_4)), 
                   color="black", fill="white") +
                  labs(subtitle = "Sibling groups")

p6 <- p + geom_bar(mapping = aes(factor(boy)), 
                   color="black", fill="white") +
                  labs(subtitle = "Gender")
 
p7 <- p + geom_histogram(mapping = aes(lagscore), 
                   color="black", fill="white") +
                  labs(subtitle = "Lagscore")

p <- ggarrange(p1, p2, p3, p4, p5, p6, p7)

annotate_figure(p, 
                top = text_grob("Microcovariates (2000)",
                color = "red", face = "bold", size = 12))
```

```{r}
# Gender distribution in treated vs untreated groups
data %>% group_by(boy, treated) %>% count()
```

---

## Multivariate descriptives (Data 2001)

This part specifically looks at the relationships between multivariate variables in the sample of interest, **data_2001**.

  **School covariates**

```{r}
# Sibling categories in Arab and Religious school
data_2001 %>% group_by(school_arab, siblings_4) %>% count()
data_2001 %>% group_by(school_religious, siblings_4) %>% count()
```
```{r}
p <- ggplot(data = data_2001) + 
  scale_y_continuous(labels = scales::percent) +
  scale_x_discrete(labels=c("0" = "No", "1" = "Yes")) +
  guides(fill=guide_legend(title="")) + 
  scale_fill_discrete(labels = c("Fewer than 4","At least 4")) +
  theme_classic()

# Different graphs for 2 school types
p1 <- p + geom_bar(aes(x = factor(school_arab), 
                   y = ..count.. / sum(..count..),
                   fill = factor(siblings_4)),
                   position="fill") + 
      labs(x = "",
           y = "",
           subtitle = "Arab schools")

p2 <- p + geom_bar(aes(x = factor(school_religious), 
                   y = ..count.. / sum(..count..),
                   fill = factor(siblings_4)),
              position="fill") + 
      labs(subtitle = "Religious schools",
           x = "",
           y = "")

p <- ggarrange(p1, p2, common.legend = T, legend="bottom")

annotate_figure(p, 
                top = text_grob("Sibling groups by school type (%)",
                color = "red", face = "bold", size = 12))
```


  **Micro covariates**

```{r Parental education}
# Schooling of mother and father in 2 sibling categories
data_2001 %>% group_by(father_educ, siblings_4) %>% count()
```

```{r}
# Visualization
# Comparing school levels of mother and father between 2 sibling groups
p1 <- ggplot(data = data_2001,
       aes(x = factor(father_educ), 
           y = ..count.., 
           fill = factor(siblings_4))) + 
  geom_bar(position = "dodge" ) +
  labs(subtitle = "Father education", 
       x = "", y = "") +
  guides(fill=guide_legend(title="")) + 
  scale_fill_discrete(labels = c("Fewer than 4","At least 4")) +
  theme_classic()

p2 <- ggplot(data = data_2001,
       aes(x = factor(mother_educ), 
           y = ..count.., 
           fill = factor(siblings_4))) + 
  geom_bar(position = "dodge" ) +
  labs(subtitle = "Mother education", 
       x = "", y = "") +
  theme_classic()

p <- ggarrange(p1, p2, common.legend = T, legend="bottom", nrow = 2)

annotate_figure(p, 
                top = text_grob("Parental education (years)",
                color = "red", face = "bold", size = 12))
```

```{r Immigrantion status}
# Sibling categories between immigrants and natives
data_2001 %>% group_by(immigrant, siblings_4) %>% count()
```


```{r}
# Visualization
p <- ggplot(data = data_2001, 
       aes(x = factor(immigrant), 
           y = ..count.. / sum(..count..),
           fill = factor(siblings_4))) + 
  geom_bar(position="fill") +
  labs(x = "",
       y = "") +
  scale_y_continuous(labels = scales::percent) +
  guides(fill=guide_legend(title="")) +
  scale_fill_discrete(labels = c("Fewer than 4","At least 4")) +
  scale_x_discrete(labels=c("0" = "Girls", "1" = "Boys")) +
  theme(legend.position="bottom") +
  theme_classic()

annotate_figure(p, 
                top = text_grob("Family size of immigrants and natives",
                color = "red", face = "bold", size = 12))
```


```{r Gender}
# Gender distribution in 2 siblings categories
data_2001 %>% group_by(boy, siblings_4) %>% count()
data_2001 %>% group_by(boy) %>% count()
```

```{r}
# Visualization
p <- ggplot(data_2001, 
       aes(x = factor(boy), 
           y = ..count..,
           fill = factor(siblings_4))) +
  geom_bar() + 
  labs(x = "", 
       y = "") +
  guides(fill=guide_legend(title="")) + 
  scale_fill_discrete(labels = c("Fewer than 4","At least 4")) +
  scale_x_discrete(labels=c("0" = "Girls", "1" = "Boys")) +
  theme_classic()

annotate_figure(p, 
                top = text_grob("Family size between gender",
                color = "red", face = "bold", size = 12))
```

Students with at least 4 siblings have lower lagscore performance. However, this can be due to the size of the two sibling categories - there are more observations for the group that has fewer siblings.

```{r Lagscore}
# Lagscore distribution in 2 siblings groups
list ("fewer than 4 siblings" = with(data_2001 %>% 
                                       filter(siblings_4 == 0), 
                                     summary(lagscore)),
      
      "at least 4 siblings" = with(data_2001 %>% 
                               filter(siblings_4 == 1), 
                               summary(lagscore)))
```

```{r}
# Visualization
p <- ggplot(data_2001, 
       aes(x = factor(siblings_4), y = lagscore, 
           fill = factor(siblings_4))) +
  geom_boxplot() + 
  labs(x = "",
       y = "") +
  guides(fill=guide_legend(title="")) + 
  scale_fill_discrete(labels = c("Fewer than 4","At least 4")) + 
  scale_x_discrete(labels=c("0" = "", "1" = "")) +
  theme_minimal()

annotate_figure(p, 
                top = text_grob("Lag score per sibling category",
                color = "red", face = "bold", size = 12))
```


  **Correlation Matrices**

We draw correlation matrices for all numeric variables in the data_2001. A correlation plot of variables used for the regression in **Table 2: Panel_2001** and several correlation suplots are the provided to describe the relationship between school covariates and micro covariates to the outcome variable.

We observe that:

    * Moderately negative correlations between parents' education and number of children (siblings)
    
    * Correlation between number of siblings and bagrut status is almost 0.
    
    * A weakly negative relation between family size and students' lagged scores.
    

```{r Correlation table}
# Pearson correlation
cor_data_2001 <- data_2001 %>% 
  mutate(sib_category = as.numeric(sib_category)) %>%
  select (-c("pair", "school_id", "year")) %>% 
  cor() %>%
  round(4)
```

```{r}
# Correlation plot for all numeric variables in data_2001
corPlot(cor_data_2001,
        main = "Correlation",
        cex = 0.5,
        xlas = 2)
```

```{r}
# Correlation plot for variables of interest in data_2001
corPlot(data_2001 %>% 
          select(treated, school_religious, school_arab, 
                 boy, immigrant, father_educ, mother_educ,  
                 bagrut_status, lagscore, siblings_4, 
                 ls_25, ls_50, ls_75, ls_100),
        main = "Correlation",
        cex = 0.5,
        xlas = 2)
```

```{r}
# Correlation subplots

  # School covariates
corPlot(data_2001 %>% 
          select(bagrut_status, treated, school_religious, school_arab),
        main = "School covariates", 
        cex = 0.5)

  # Micro covariates
corPlot(data_2001 %>% 
          select(bagrut_status, treated, boy, immigrant, 
                 father_educ, mother_educ,  
                 bagrut_status, lagscore, siblings_4, 
                 ls_25, ls_50, ls_75, ls_100
                 ),
        main = "Micro covariates",
        cex = 0.5,
        xlas = 2)
```

---