---
title: 'Section 4: Internal Validity (Lisa)'
author: "Lan Nguyen (6687547) | Lisa Verlare (6929699) | Nguyen Thuy Duong (6827209)"
output: 
  html_document:
    toc: true
    toc_depth: 3
    toc_float: true
    number_sections: true
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = F)
```


```{r packages, include=FALSE}
library(haven)
library(tidyverse)
library(dplyr)
library(clubSandwich)
library(kableExtra)
library(vtable)
library(ggpubr)
library(gridExtra)
library(ggplot2)
library(Hmisc) # statistic table format 
library(strucchange)  #Chow test
library(margins) # logit marginal effect
library(sandwich) # correct downward-biased standard errors
library(corrplot)
library(RColorBrewer)
library(webshot)
# webshot::install_phantomjs()
library(magick)
library(psych)
library(ggpubr)
```

```{r}
# loading the data sets into the environment
data_1999 <- readRDS(file = "data/data_1999.Rda")
data_2000 <- readRDS(file = "data/data_2000.Rda")
data_2001 <- readRDS(file = "data/data_2001.Rda")
data_2002 <- readRDS(file = "data/data_2002.Rda")
```


The first part of this section describes a replicated table of the Covariate Balance for **Panel A. 2001** and **Panel B. 2000** of Table A2. We replicate the original covariate balance table provided by the authors in table A2 for both the years 2001 and 2000. We conclude this part by producing the corresponding table.

# Panel A. 2001
```{r}
# create a data frame to put in the means and standard errors
table_a2_2001 <- data.frame(NULL)

# every variable for which the covariate needs to be calculated
varlist <- c(
  "school_arab", "school_religious", "father_educ", "mother_educ", 
  "siblings", "immigrant", "lagscore"
  )
```

```{r}
# for loop that calculates the mean and differences between control and 
# treatment group and its standard errors

# All
for(i in 1:7){
  
  # mean of the column 
  e_mean <- mean(data_2001[[varlist[i]]])
  
  # linear regression on a variable from varlist
  x <- lm(as.formula(paste(varlist[[i]], "~ treated")), data = data_2001)
  
  # clustered standard errors
  y <- coef_test(obj = x, cluster = data_2001$school_id, vcov = "CR1")
  
  # assigning values to the table
  table_a2_2001[i, 1] <- e_mean
  table_a2_2001[i, 2] <- y[2,2]
  table_a2_2001[i, 3] <- y[2,3]
  }
```

```{r}
# for loop that calculates the mean and differences between control and 
# treatment group and its standard errors

# Boys
for (i in 1:7){
  
    # mean of the column 
    e_mean <- mean(subset(data_2001, boy == 1)[[varlist[i]]])
    
    # linear regression
    x <- lm(
    as.formula(paste(varlist[[i]], "~ treated")), 
    data = subset(data_2001, boy == 1)
    )
    
    # clustered standard errors
    y <- coef_test(
    obj = x, 
    cluster = subset(data_2001, boy == 1)$school_id, 
    vcov = "CR1"
    )
    
  # assigning values to the table
  table_a2_2001[i, 4] <- e_mean
  table_a2_2001[i, 5] <- y[2,2]
  table_a2_2001[i, 6] <- y[2,3]
  }
```

```{r}
# for loop that calculates the mean and differences between control and 
# treatment group and its standard errors

# Girls
for (i in 1:7){
    
    # mean of the column 
    e_mean <- mean(subset(data_2001, boy == 0)[[varlist[i]]])
    
    # linear regression
    x <- lm(
      as.formula(paste(varlist[[i]], "~ treated")), 
      data = subset(data_2001, boy == 0)
      )
    
    # clustered standard errors
    y <- coef_test(
      obj = x, 
      cluster = subset(data_2001, boy == 0)$school_id, 
      vcov = "CR1"
      )
    
    # assigning values to the table
    table_a2_2001[i, 7] <- e_mean
    table_a2_2001[i, 8] <- y[2,2]
    table_a2_2001[i, 9] <- y[2,3]
  }
```

Next, we format our table.
```{r}
# renaming the data frame columns
colnames(table_a2_2001) <- c(
  "Mean All", "Difference All", "SE All", 
  "Mean Boys", "Difference Boys", "SE Boys", 
  "Mean Girls", "Difference Girls", "SE Girls"
  )

# renaming the data frame rows
rownames(table_a2_2001) <- c(
  "school_arab", "school_religious", "father_educ", "mother_educ", 
  "siblings", "immigrant", "lagscore"
  )

# Rounding the values in the data frame to 3 decimals
table_a2_2001 <- round(table_a2_2001, 3)
```

# Panel B. 2000
```{r}
# create a data frame to put in the means and standard errors
table_a2_2000 <- data.frame(NULL)

# every variable for which the covariate needs to be calculated
varlist2 <- c(
  "bagrut_status", "school_arab", "school_religious", "father_educ", 
  "mother_educ", "siblings", "immigrant", "lagscore"
  )
```

```{r}
# for loop that calculates the differences between control and treatment group
# and the standard errors

# All
for(i in 1:8){
  
  # mean of the column 
  e_mean <- mean(data_2000[[varlist2[i]]])
  
  # linear regression
  x <- lm(as.formula(paste(varlist2[[i]], "~ treated")), data = data_2000)
  
  # clustered standard errors
  y <- coef_test(obj = x, cluster = data_2000$school_id, vcov = "CR1")
  
  # assigning values to the table
  table_a2_2000[i, 1] <- e_mean
  table_a2_2000[i, 2] <- y[2,2]
  table_a2_2000[i, 3] <- y[2,3]
  }
```

```{r}
# for loop that calculates the differences between control and treatment group
# and the standard errors

# Boys
for (i in 1:8){
  
    # mean of the column 
    e_mean <- mean(subset(data_2000, boy == 1)[[varlist2[i]]])
    
    # linear regression
    x <- lm(
    as.formula(paste(varlist2[[i]], "~ treated")), 
    data = subset(data_2000, boy == 1)
    )
    
    # clustered standard errors
    y <- coef_test(
    obj = x, 
    cluster = subset(data_2000, boy == 1)$school_id, 
    vcov = "CR1"
    )
    
  # assigning values to the table
  table_a2_2000[i, 4] <- e_mean
  table_a2_2000[i, 5] <- y[2,2]
  table_a2_2000[i, 6] <- y[2,3]
  }
```

```{r}
# for loop that calculates the differences between control and treatment group
# and the standard errors

# Girls
for (i in 1:8){
  
  # mean of the column 
    e_mean <- mean(subset(data_2000, boy == 0)[[varlist2[i]]])
    
    # linear regression
    x <- lm(
      as.formula(paste(varlist2[[i]], "~ treated")), 
      data = subset(data_2000, boy == 0)
      )
    
    # clustered standard errors
    y <- coef_test(
      obj = x, 
      cluster = subset(data_2000, boy == 0)$school_id, 
      vcov = "CR1"
      )
    
    # assigning values to the table
    table_a2_2000[i, 7] <- e_mean
    table_a2_2000[i, 8] <- y[2,2]
    table_a2_2000[i, 9] <- y[2,3]
  }
```

Next, we format our table.
```{r}
# renaming the data frame columns
colnames(table_a2_2000) <- c(
  "Mean All", "Difference All", "SE All", 
  "Mean Boys", "Difference Boys", "SE Boys", 
  "Mean Girls", "Difference Girls", "SE Girls"
  )

# renaming the data frame rows
rownames(table_a2_2000) <- c(
  "bagrut_status", "school_arab", "school_religious", "father_educ", 
  "mother_educ", "siblings", "immigrant", "lagscore"
  )

# Rounding the values in the data frame to 3 decimals
table_a2_2000 <- round(table_a2_2000, 3)
```

# Translating into a Table
```{r}
## 2001
# We loop over the rows to put the standard errors in the same cell as the 
# differences.
# This is how we will format the table with a coefficient and below it 
# the standard error
for (i in 1:7){
  table_a2_2001[i, 2] <- paste(
    table_a2_2001[i, 2], "<br>(", table_a2_2001[i, 3], ")", sep = ""
    )
  table_a2_2001[i, 5] <- paste(
    table_a2_2001[i, 5], "<br>(", table_a2_2001[i, 6], ")", sep = ""
    )
  table_a2_2001[i, 8] <- paste(
    table_a2_2001[i, 8], "<br>(", table_a2_2001[i, 9], ")", sep = ""
    )
}

# generate line breaks in the cell between the coefficient and standard error
table_a2_2001[, 2] <- linebreak(table_a2_2001[, 2])
table_a2_2001[, 5] <- linebreak(table_a2_2001[, 5])
table_a2_2001[, 8] <- linebreak(table_a2_2001[, 8])

# delete the columns of the standard errors that are now included in the 
# difference columns
table_a2_2001 <- table_a2_2001 %>%
 dplyr::select(-3, -6, -9)

## 2000
# We loop over the rows to put the standard errors in the same cell as the 
# differences.
# This is how we will format the table with a coefficient and below it 
# the standard error
for (i in 1:8){
  table_a2_2000[i, 2] <- paste(
    table_a2_2000[i, 2], "<br>(", table_a2_2000[i, 3], ")", sep = ""
    )
  table_a2_2000[i, 5] <- paste(
    table_a2_2000[i, 5], "<br>(", table_a2_2000[i, 6], ")", sep = ""
    )
  table_a2_2000[i, 8] <- paste(
    table_a2_2000[i, 8], "<br>(", table_a2_2000[i, 9], ")", sep = ""
    )
}

# generate line breaks in the cell between the coefficient and standard error
table_a2_2000[, 2] <- linebreak(table_a2_2000[, 2])
table_a2_2000[, 5] <- linebreak(table_a2_2000[, 5])
table_a2_2000[, 8] <- linebreak(table_a2_2000[, 8])

# delete the columns of the standard errors that are now included in the 
# difference columns
table_a2_2000 <- table_a2_2000 %>%
  dplyr::select(-3, -6, -9)

# Merging the tables for each year into one table
table_a2 <- rbind(table_a2_2001, table_a2_2000)

# Changing the row names
rownames(table_a2) <- c(
  "Arab school", "Religious school", "Father's education", "Mother's education", 
  "Number of siblings", "Immigrant", "Lagged score", "Bagrut rate", 
  "Arab school ", "Religious school ", "Father's  education ", 
  "Mother's education ", "Number of siblings ", "Immigrant ", "Lagged score "
  )

# Creating the table
table_a2 %>%
  kable(
    format = "html",
    escape = FALSE,
    caption = "<b>Table 3: Covariate Balance</b>",
    col.names = c(
        "Mean", "Differences", "Mean", "Differences", "Mean", "Differences"
        ),
    align = "l"
    ) %>%
  kable_classic(
    full_width = F, html_font = "Times New Roman", position = "left"
    ) %>%
  add_header_above(c(" " = 1, "All" = 2, "Boys" = 2, "Girls" = 2)) %>%
  
  # Panel A
  pack_rows("Year: 2001", 1, 7, italic = TRUE, bold = FALSE) %>%  
  pack_rows("School covariates", 1, 2) %>%
  pack_rows("Micro covariates", 3, 7) %>%
  
  # Panel B
  pack_rows("Year: 2000", 8, 15, italic = TRUE, bold = FALSE) %>%
  pack_rows("School covariates", 9, 10) %>%
  pack_rows("Micro covariates", 11, 15) %>%
  
  # Adding footnotes for the table
  footnote(
    general = c(
      "Table columns report means and differences between the treatment and control group. Standard errors are clustered at the school level and reported in parantheses.",
      "This is a replication of Table B3 (Angrist & Lavy, 2009, p. 1410)"
      ), 
    footnote_as_chunk = T
  )

```
